Investigating Bicycle Theft in Toronto: Trends and Patterns

### 2024-09-26 paper/paper.qmd
updated links to repo and citations

---
title: "Investigating Bicycle Theft in Toronto: Trends and Patterns"
subtitle: "."
author: 
  - Taejun Um
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "In urban environments like Toronto, bicycle theft is as common as in any major city worldwide. This paper examines the trends and patterns of bicycle theft in Toronto from 2014 to 2022, focusing on the cost of bicycles and the types of locations where the thefts occurred. Data from this period show that the overall number of bicycle thefts did not significantly decline but began to decrease gradually from 2020, particularly in thefts occurring at residential properties and those involving high-end bicycles. These findings can inform community efforts and assist Toronto's public authorities in developing more effective strategies to protect citizens' property and reduce bicycle theft."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
library(opendatatoronto)
library(knitr)

@@

Toronto is the most populous and densely populated city in Canada. As a result, traffic congestion makes it difficult for people to navigate the city, and many citizens report this as a significant issue*. This has led to an increase in the number of cyclists using bicycles for efficient point-to-point travel within the city. Currently, approximately 659 km of cycling routes are interwoven like a spider's web throughout Toronto*. Unfortunately, bicycle thefts remain a persistent problem for residents.

@@

The dataset was downloaded from OpenDataToronto, and its setup was completed with the help of tidyverse, janitor, and tidyr.

The original dataset contained 28 variables, but I used the following: ID, occurrence date, occurrence year, occurrence month, premises type, and bike cost. Then, I created a new group called "cost group" based on the bike cost, categorizing the bicycles according to their price range. Since the dataset is based on the date the theft was reported, I organized the data by the actual date of occurrence to reflect events from 2014 to 2022, excluding incidents that occurred before 2014. Additionally, during the data cleaning phase, observations with missing information were excluded. As a result, the dataset used in this paper contains 30,937 observations. (@tbl-head) shows an first 5 row of the data used.

>>>>

---
title: "Investigating Bicycle Theft in Toronto: Trends and Patterns"
author: 
  - Taejun Um
thanks: "Code and data are available at: https://github.com/tonytto/Investigating-Bicycle-Theft-in-Toronto"
date: today
date-format: long
abstract: "In urban environments like Toronto, bicycle theft is as common as in any major city worldwide. This paper examines the trends and patterns of bicycle theft in Toronto from 2014 to 2022, focusing on the cost of bicycles and the types of locations where the thefts occurred. Data from this period show that the overall number of bicycle thefts did not significantly decline but began to decrease gradually from 2020, particularly in thefts occurring at residential properties and those involving high-end bicycles. These findings can inform community efforts and assist Toronto's public authorities in developing more effective strategies to protect citizens' property and reduce bicycle theft."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(opendatatoronto)
library(knitr)

@@

Toronto is the most populous and densely populated city in Canada. As a result, traffic congestion makes it difficult for people to navigate the city, and many citizens report this as a significant issue [@traffic]. This has led to an increase in the number of cyclists using bicycles for efficient point-to-point travel within the city. Currently, approximately 659 km of cycling routes are interwoven like a spider's web throughout Toronto [@bikelane]. Unfortunately, bicycle thefts remain a persistent problem for residents.

@@

The dataset was downloaded from Toronto's Open Data Portal using opendatatoronto package [@opendatatoronto]. Its setup was completed through R [@citeR] with the help of tidyverse package [@citetidyverse], janitor package [@citejanitor] and knitr package [@citeknitr].

The original dataset contained 28 variables, but I used the following: ID, occurrence date, occurrence year, occurrence month, occurrence hour, premises type, and bike cost. Then, I created a new group called "cost group" based on the bike cost, categorizing the bicycles according to their price range. Since the dataset is based on the date the theft was reported, I organized the data by the actual date of occurrence to reflect events from 2014 to 2022, excluding incidents that occurred before 2014. Additionally, during the data cleaning phase, observations with missing information were excluded. As a result, the dataset used in this paper contains 29,217 observations. (@tbl-head) shows an first 5 row of the data used.
